
\section{3000Copy Sequence of Operations}
%% * 3000copy (mmap & rw), sequence of operations
In all cases, we perform the following initalization steps:
\begin{enumerate}
\item Parse the source and destination args
\item Open the source and dest files, get the file descriptors
\end{enumerate}

\subsection{RW Implementation}
\begin{csrc}
done = 0;
while (!done) {
        len = read(source_fd, buf, BUFSIZE);
        if (len == -1) {
                report_error("reading source", strerror(errno));
        }

        if (len > 0) {
                if (write(dest_fd, buf, len) == -1) {
                        report_error("writing dest", strerror(errno));
                }
        } else {
                done = 1;
        }
}
\end{csrc}
\begin{enumerate}
\item Read in a maximum of BUFSIZE bytes into our buffer, take note of how many
  bytes we read
\item If we have bytes, write them to the destination file
\item Else we are done! Close file descriptors.
\end{enumerate}

\subsection{MMAP Implementation}
\begin{csrc}
        len = statbuf.st_size;
        source_map = (char *) mmap(NULL, len,
                                   PROT_READ, MAP_SHARED, source_fd, 0);

        if (source_map == MAP_FAILED) {
                report_error("source map", strerror(errno));
        }

        if (stat(dest_fn, &statbuf) == -1) {
                printf("%s does not exist, creating\n", dest_fn);
        } else {
                printf("%s exists, overwriting\n", dest_fn);
        }

        //... repeat the above for the dest FD

        printf("Copying bytes...\n");

        for (i = 0; i < len; i++) {
                dest_map[i] = source_map[i];
        }
\end{csrc}
\begin{enumerate}
\item Open the source and dest file, get the file descriptors.
\item Get the length of the source file. Create a mapping the size of the source
  file into virtual memory using the FD we got from opening the source file.
\item Get the length of the dest file. Create a mapping of the size of the dest
  file into virtual memory using the FD we got from opening the dest file.
\item Iterate over the source map, transferring its values to the destination
  map.
\item Close the file descriptors
\end{enumerate}

