
\section{Hard Links vs Symlinks}
%% * hard links versus symbolic links

\subsection{Hard Links}
A hard link can be thought of as a second filename. For example, inode $x$ can
have filename \texttt{blah.txt} when it's created, but if I hardlink
\texttt{blah.txt} to \texttt{notblah.txt} I'm just updating that inode's record
with two names: \texttt{blah.txt} and \texttt{notblah.txt}

Hard linking is done by \texttt{ln source dest}. A hardlink appears as a
copy of a file, but editing it edits both filenames (since they link to the same
inode).

Hard links, because of how they're created, are hard to tell from regular files
(since they are also regular files). In the below example I created file.txt,
and ass.txt which hardlinks to file.txt

\begin{verbatim}
$ ls -al
total 8
drwxr-xr-x 1 conner users 30 Oct 12 16:08 .
drwxr-xr-x 1 conner users 52 Oct 12 16:07 ..
-rw-r--r-- 2 conner users 15 Oct 12 16:10 ass.txt
-rw-r--r-- 2 conner users 15 Oct 12 16:10 file.txt
\end{verbatim}

Hmm, these appear to be the same. A simple way to tell if a hardlink exists is
to look at the \textbf{inode} that it corresponds to. This can be done with
\texttt{ls -i} 

\begin{verbatim}
$ ls -li
total 8
1471517 -rw-r--r-- 2 conner users 15 Oct 12 16:10 ass.txt
1471517 -rw-r--r-- 2 conner users 15 Oct 12 16:10 file.txt
\end{verbatim}
Because the inodes for those two files are the same, we know that they are
hardlinked together.

\subsection{Soft Links}
A soft link, or symlink, can be thought of as a pointer to an inode. The
difference between a symlink and a hard link is that this \textbf{not} another
name added to an existing file, rather, it's a new file that points to the inode
of another file. This means that the source file has to exist in order for the
symlink to be valid.

Symlinks are created by \texttt{ln -s source dest}, and dest will have a new
inode that points to the source file. See below for an example

Here, I created \texttt{link} which points to \texttt{file.txt}
\begin{verbatim}
$ ls -al
drwxr-xr-x 1 conner users 24 Oct 12 16:16 .
drwxr-xr-x 1 conner users 52 Oct 12 16:07 ..
-rw-r--r-- 1 conner users 15 Oct 12 16:10 file.txt
lrwxrwxrwx 1 conner users  8 Oct 12 16:16 link -> file.txt
\end{verbatim}

We know right away that it's an symlink because of the arrow in ls, and we can
verify the symlink resides on another inode from \texttt{ls -i}

\begin{verbatim}
$ ls -li
total 8
1471517 -rw-r--r-- 1 conner users 15 Oct 12 16:10 file.txt
1471741 lrwxrwxrwx 1 conner users  8 Oct 12 16:16 link -> file.txt
\end{verbatim}

